Evaluate PEER in each cohort and brain region

### 2021-02-18 combined_analysis/eval_resid_in_each.Rmd
add more summary info

cd /hpc/users/hoffmg01/work/covarr-de
# rm -rf molec_profiling_cache/
ml git pandoc R/3.6.3 # to get peer
git pull
R

@@

# When individuals were sequenced multiple times from the same brain region
#   for technical replicates or QC failure,
# Keep sample with most reads
METADATA = METADATA %>%
  group_by(Individual_ID, Region) %>% 
  slice_max(MappedReads)
```

>>>>

cd /hpc/users/hoffmg01/work/covarr-de
# rm -rf combined_analysis/eval_resid_in_each_cache/
ml git pandoc R/3.6.3 # to get peer
git pull
R

@@

# When individuals were sequenced multiple times from the same brain region
#   for technical replicates or QC failure,
# Keep sample with most reads
METADATA = METADATA %>%
  group_by(Individual_ID, Region, Cohort) %>% 
  slice_max(MappedReads)
```
